NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-05 Manuscript/manuscriptPS.tex

\begin{figure}[!tb]
  \centering
  \includegraphics[width=8.5cm]{../Figs/fig1_POPS.pdf}
  \caption{\label{PShgSIGNSsimpson}
    The headgroup and glycerol backbone region of the (A) INEPT spectrum and
    (B) 2D R-PDLF spectra.
    (C) Experimental SDROSS data (points) and SIMPSON simulations (blue lines) with
    the order parameter values of -0.12 for the $\beta$-carbon, and 0.09 and -0.02
    for the $\alpha$-carbon slittings. The S-DROSS curve from SIMPSON simulation with positive value
    for the smaller $\alpha$-carbon order parameter (dashed grey).
  }
  \todo{I think that the peak labeling would be good to show also in (A).}
\end{figure}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PCPScomp-eps-converted-to.pdf}
  \caption{\label{HGorderParameters}
    (A) Chemical structures and labels for the headgroup and glycerol backbone carbons.
    (B) Headgroup and glycerol backbone order parameters of POPS measured in this work compared
    with the previously published values from DOPS ($^2$H NMR, 0.1M of NaCl) \cite{browning80} and 
    POPC  ($^{13}$C NMR) \cite{ferreira13} experiments. Signs of the PS order parameters
    are measured in this work. Signs of the PC order parameters are measured previously~\cite{ferreira16}.
  }\todo{
  1) Use diamonds for DOPS, spheres for POPS.
  2) Error bars?
  3) Change the y-label to $S_\mathrm{CH}$, and invert the y-axis, as in Fig. 3.
  4) Make lower g1 POPC visible, e.g., by slightly larger point.
  }
\end{figure}

>>>>

\begin{figure}[!tb]
  \centering
  \includegraphics[width=8.5cm]{../Figs/fig1_POPS.pdf}
  \caption{\label{PShgSIGNSsimpson}
    The headgroup and glycerol backbone region of the (A) INEPT spectrum and
    (B) 2D R-PDLF spectra.
    (C) Experimental S-DROSS data (points), and SIMPSON simulations (blue lines) with
    the order parameter values of -0.12 for the $\beta$-carbon, and 0.09 and -0.02
    for the $\alpha$-carbon splittings.
    Dashed gray line is the S-DROSS curve from a SIMPSON simulation with a positive value (+0.02) 
    for the smaller $\alpha$-carbon order parameter.
  }
  \todo{I think that the peak labeling would be good to show also in (A).}\\
  \todo{Also for $\alpha$ these are OPs, right,  thus we could just exclude the word 'splittings'?}
  \todo{Please confirm: Was the positive value used for $\alpha$ in the gray curve 0.02?}
\end{figure}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PCPScomp-eps-converted-to.pdf}
  \caption{\label{HGorderParameters}
    (A) Chemical structures and labels for the headgroup and glycerol backbone carbons.
    (B) Headgroup and glycerol backbone order parameters of POPS measured in this work compared
    with the previously published values from DOPS ($^2$H NMR, 0.1M of NaCl) \cite{browning80} and 
    POPC  ($^{13}$C NMR) \cite{ferreira13} experiments. Signs of the PS order parameters
    are measured in this work. Signs of the PC order parameters are measured previously~\cite{ferreira16}.
  }\todo{
  1) Use diamonds for DOPS, spheres for POPS.
  2) Error bars?
  3) Change the y-label to $S_\mathrm{CH}$, and invert the y-axis, as in Fig. 3.
  4) Make lower g1 POPC visible, e.g., by slightly larger point.
  }
\end{figure}
